Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test

### 2019-09-13 paper.tex
FIX formatting

\documentclass{article}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.45in]{geometry}
\usepackage[round]{natbib}

@@

\begin{equation}
\underline{\beta}(\rho)=\widehat{\beta}(\rho)+\frac{T-2}{2} \frac{\widehat{\sigma_{ue}}}{\widehat{\sigma}_{e} \widehat{\omega}}\left(\frac{\widehat{\omega}^{2}}{\widehat{\sigma}_{v}^{2}}-1\right) \operatorname{SE}(\widehat{\rho})^{2}-1.645\left(1-\widehat{\delta}^{2}\right)^{1 / 2} \operatorname{SE}(\widehat{\beta})
\end{equation}
and 
\begin{equation}
\overline{\beta}(\rho)=\widehat{\beta}(\rho)+\frac{T-2}{2} \frac{\widehat{\sigma}_{u e}}{\widehat{\sigma}_{e} \widehat{\omega}}\left(\frac{\widehat{\omega}^{2}}{\widehat{\sigma}_{v}^{2}}-1\right) \operatorname{SE}(\widehat{\rho})^{2}+1.645\left(1-\widehat{\delta}^{2}\right)^{1 / 2} \operatorname{SE}(\widehat{\beta})
\end{equation}
A 5\% one-sided or 10\% two-sided test of $H_0: \beta = 0$ is based on the 90\% Bonferroni confidence interval
$$[\underline{\beta}(\overline{\rho}), \overline{\beta}(\underline{\rho})]$$
\subsection{Power comparison}
\label{power}
\citet{campbell2006efficient} evaluate the power of the feasible Q-test under local-to-unity asymptotics. In this framework, the OLS estimators $\hat{\beta}$ and $\hat{\rho}$ are consistent at rate $T$. Thus, to have a meaningful comparison, local alternatives of the form $\beta = \beta_0 + b/T$ are considered where $b$ is a constant. The feasible Q-test is found to dominate the feasible t-test in all cases considered with increasing relative power gain in increasing $|\delta|$ and decreasing $|c|$. Their analysis shows that in the case of a highly persistent regressor, using the Q-test over the t-test provides a comparatively important gain in power. Their numerical refinement of the Bonferroni method provides a substantial further gain in power for the Q-test since this test exploits information about $\rho$. This makes its confidence interval for $\beta$ given $\rho$ more sensitive to $\rho$. Hence, without the refinement the Bonferroni Q-test is too conservative.

@@

\begin{threeparttable}
\begin{tabular}{rrrrrrrr}
 \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.95 & 0.4160 & 0.0826 & 0.0483 \\ 
  2 & 50 & 0 & 1.000 & -0.75 & 0.2916 & 0.0837 & 0.0515 \\ 
  3 & 50 & -2 & 0.961 & -0.95 & 0.2714 & 0.0868 & 0.0482 \\ 
  4 & 50 & -2 & 0.961 & -0.75 & 0.2079 & 0.0881 & 0.0532 \\ 
  5 & 50 & -20 & 0.608 & -0.95 & 0.0977 & 0.1206 & 0.0515 \\ 
  6 & 50 & -20 & 0.608 & -0.75 & 0.0840 & 0.1078 & 0.0484 \\ 
  7 & 100 & 0 & 1.000 & -0.95 & 0.4217 & 0.0616 & 0.0480 \\ 
  8 & 100 & 0 & 1.000 & -0.75 & 0.2930 & 0.0616 & 0.0497 \\ 
  9 & 100 & -2 & 0.980 & -0.95 & 0.2698 & 0.0587 & 0.0505 \\ 
  10 & 100 & -2 & 0.980 & -0.75 & 0.2104 & 0.0588 & 0.0489 \\ 
  11 & 100 & -20 & 0.802 & -0.95 & 0.1063 & 0.0622 & 0.0471 \\ 
  12 & 100 & -20 & 0.802 & -0.75 & 0.0874 & 0.0514 & 0.0500 \\ 
  13 & 250 & 0 & 1.000 & -0.95 & 0.4259 & 0.0476 & 0.0483 \\ 
  14 & 250 & 0 & 1.000 & -0.75 & 0.2970 & 0.0506 & 0.0536 \\ 
  15 & 250 & -2 & 0.992 & -0.95 & 0.2866 & 0.0507 & 0.0481 \\ 
  16 & 250 & -2 & 0.992 & -0.75 & 0.2092 & 0.0466 & 0.0492 \\ 
  17 & 250 & -20 & 0.920 & -0.95 & 0.1080 & 0.0406 & 0.0517 \\ 
  18 & 250 & -20 & 0.920 & -0.75 & 0.0944 & 0.0369 & 0.0501 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 

@@

 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 

@@

\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with non local to unity autoregressive root. 10,000 Monte Carlo simulations are performed.

@@

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
\citet*{glosten1993relation} [GJR] observe that in financial markets, negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by the conditional variance of a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$, negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis, $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability. Even for the larger sample size of 100, the amount of over-rejection of the right-tailed Q-test at 5\% significance level surpasses 50\%. The null for the smaller sample size is over-rejected more than 100\%.

\begin{table}[h!]
\centering
\caption{Finite-sample rejection rates (common stochastic trend GJR-GARCH)}
\label{tab:mc_grj-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.95 & 0.2836 & 0.1001 & 0.1033 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.90 & 0.2736 & 0.0946 & 0.0986 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.80 & 0.2635 & 0.0952 & 0.0993 \\ 
  4 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.95 & 0.3054 & 0.0757 & 0.0802 \\ 
  5 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.90 & 0.2811 & 0.0662 & 0.0727 \\ 
  6 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.80 & 0.2801 & 0.0685 & 0.0734 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GJR-GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\documentclass[11pt, a4paper]{article}
\usepackage[onehalfspacing]{setspace}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.25in]{geometry}
\usepackage[round]{natbib}

@@

\begin{equation}
\underline{\beta}(\rho)=\widehat{\beta}(\rho)+\frac{T-2}{2} \frac{\widehat{\sigma_{ue}}}{\widehat{\sigma}_{e} \widehat{\omega}}\left(\frac{\widehat{\omega}^{2}}{\widehat{\sigma}_{v}^{2}}-1\right) \operatorname{SE}(\widehat{\rho})^{2}-1.645\left(1-\widehat{\delta}^{2}\right)^{1 / 2} \operatorname{SE}(\widehat{\beta})
\end{equation}
and 
\begin{equation}
\overline{\beta}(\rho)=\widehat{\beta}(\rho)+\frac{T-2}{2} \frac{\widehat{\sigma}_{u e}}{\widehat{\sigma}_{e} \widehat{\omega}}\left(\frac{\widehat{\omega}^{2}}{\widehat{\sigma}_{v}^{2}}-1\right) \operatorname{SE}(\widehat{\rho})^{2}+1.645\left(1-\widehat{\delta}^{2}\right)^{1 / 2} \operatorname{SE}(\widehat{\beta})
\end{equation}
A 5\% one-sided or 10\% two-sided test of $H_0: \beta = 0$ is based on the 90\% Bonferroni confidence interval
$$[\underline{\beta}(\overline{\rho}), \overline{\beta}(\underline{\rho})].$$
\subsection{Power comparison}
\label{power}
\citet{campbell2006efficient} evaluate the power of the feasible Q-test under local-to-unity asymptotics. In this framework, the OLS estimators $\hat{\beta}$ and $\hat{\rho}$ are consistent at rate $T$. Thus, to have a meaningful comparison, local alternatives of the form $\beta = \beta_0 + b/T$ are considered where $b$ is a constant. The feasible Q-test is found to dominate the feasible t-test in all cases considered with increasing relative power gain in increasing $|\delta|$ and decreasing $|c|$. Their analysis shows that in the case of a highly persistent regressor, using the Q-test over the t-test provides a comparatively important gain in power. Their numerical refinement of the Bonferroni method provides a substantial further gain in power for the Q-test since this test exploits information about $\rho$. This makes its confidence interval for $\beta$ given $\rho$ more sensitive to $\rho$. Hence, without the refinement the Bonferroni Q-test is too conservative.

@@

\begin{threeparttable}
\begin{tabular}{rrrrrrrr}
 \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & BQ & Q-test \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.95 & 0.4160 & 0.0826 & 0.0483 \\ 
  2 & 50 & 0 & 1.000 & -0.75 & 0.2916 & 0.0837 & 0.0515 \\ 
  3 & 50 & -2 & 0.961 & -0.95 & 0.2714 & 0.0868 & 0.0482 \\ 
  4 & 50 & -2 & 0.961 & -0.75 & 0.2079 & 0.0881 & 0.0532 \\ 
  5 & 50 & -20 & 0.608 & -0.95 & 0.0977 & 0.1206 & 0.0515 \\ 
  6 & 50 & -20 & 0.608 & -0.75 & 0.0840 & 0.1078 & 0.0484 \\ 
  7 & 100 & 0 & 1.000 & -0.95 & 0.4217 & 0.0616 & 0.0480 \\ 
  8 & 100 & 0 & 1.000 & -0.75 & 0.2930 & 0.0616 & 0.0497 \\ 
  9 & 100 & -2 & 0.980 & -0.95 & 0.2698 & 0.0587 & 0.0505 \\ 
  10 & 100 & -2 & 0.980 & -0.75 & 0.2104 & 0.0588 & 0.0489 \\ 
  11 & 100 & -20 & 0.802 & -0.95 & 0.1063 & 0.0622 & 0.0471 \\ 
  12 & 100 & -20 & 0.802 & -0.75 & 0.0874 & 0.0514 & 0.0500 \\ 
  13 & 250 & 0 & 1.000 & -0.95 & 0.4259 & 0.0476 & 0.0483 \\ 
  14 & 250 & 0 & 1.000 & -0.75 & 0.2970 & 0.0506 & 0.0536 \\ 
  15 & 250 & -2 & 0.992 & -0.95 & 0.2866 & 0.0507 & 0.0481 \\ 
  16 & 250 & -2 & 0.992 & -0.75 & 0.2092 & 0.0466 & 0.0492 \\ 
  17 & 250 & -20 & 0.920 & -0.95 & 0.1080 & 0.0406 & 0.0517 \\ 
  18 & 250 & -20 & 0.920 & -0.75 & 0.0944 & 0.0369 & 0.0501 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for the right-tailed Bonferroni Q-test [BQ] of predictability at $\alpha$=0.05. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

 & Obs & $c$ & $\rho$ & $\delta$ & t-test & BQ& Q-test & BQ$_{{2sided}}$ \\ 

@@

 & Obs & $c$ & $\rho$ & $\delta$ & t-test & BQ & Q-test & BQ$_{{2sided}}$ \\ 

@@

\item This Table displays the finite-sample rejection rates of the true null for right-tailed  [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with non local to unity autoregressive root. 10,000 Monte Carlo simulations are performed.

@@

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
\citet*{glosten1993relation} [GJR] observe that in financial markets, negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by the conditional variance of a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$, negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis, $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability. Even for the larger sample size of 100, the amount of over-rejection of the right-tailed Q-test at 5\% significance level surpasses 50\%. The null for the smaller sample size is over-rejected more than 100\%. For very large sample sizes of more than 1000 observations, a single spike of over-rejection is found when the GARCH process is very near nonstationary. Otherwise, rejection rates are close to the nominal size.

\begin{table}[h!]
\centering
\caption{Finite-sample rejection rates (common stochastic trend GJR-GARCH)}
\label{tab:mc_grj-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.95 & 0.2836 & 0.1001 & 0.1033 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.90 & 0.2736 & 0.0946 & 0.0986 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.80 & 0.2635 & 0.0952 & 0.0993 \\ 
  4 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.95 & 0.3054 & 0.0757 & 0.0802 \\ 
  5 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.90 & 0.2811 & 0.0662 & 0.0727 \\ 
  6 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.80 & 0.2801 & 0.0685 & 0.0734 \\ 
  7&1000 & -2 & 0.998 & -0.9500 & 0.0000 & 0.95 & 0.4619 & 0.1065 & 0.1124 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GJR-GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}
